### 2025-07-10 factor-analysis.qmd
20250710 - fix library loading

```{r}
library("psych")
library("nFactors")
library("lavaan")
library("lavaangui")
library("tidyverse")
```

>>>>

library("psych")
library("nFactors")
library("lavaan")
library("lavaanPlot")
library("lavaangui")
library("tidyverse")
```

# Don't load lavaangui (b/c not installed)
library("psych")
library("nFactors")
library("lavaan")
library("lavaanPlot")
library("tidyverse")
```
